\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{geometry}

\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


\geometry{
    a4paper,
    left=0.5cm,
    right=0.5cm,
    top=1.5cm,
    bottom=0.5cm,
}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-9pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1


% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {\color{darkgray}{#1} \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \footnotesize {#2}\\
      \textit{\small#3} & \textit{\footnotesize  #4} \\
    \end{tabular*}\vspace{-1pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-1pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-1pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-1pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-1pt}}


\begin{document}


\begin{center}
    \textbf{\Huge \scshape John Doe} \\ \vspace{1pt}
    \small 123-456-7890 $|$ \href{myemail@gmail.com}{\underline{myemail@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/john-doe/}{\underline{linkedin/john-doe}} $|$
    \href{https://github.com/johndoe}{\underline{github/johndoe}}
\end{center}



\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{2020 -- 2025}
      {Bachelors of Mathematics Honours (Minor in Computing)}{Waterloo, ON}
      \resumeItemListStart
        \resumeItem{Awarded President's Scholarship}
         \resumeItem{GPA: 3.7}
        \resumeItem{Technical Product Manager at WAT.AI Club}
    \resumeItem{\textbf{Relevant Courses}: Data Structures} \\
      \resumeItemListEnd
  \resumeSubHeadingListEnd


\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C}\\ 
     \textbf{Libraries and Frameworks}{: TensorFlow}\\
     \textbf{Tools}{: Git, Docker}
    }}
 \end{itemize}



\section{Experience}
  \resumeSubHeadingListStart


    \resumeSubheading
      {\underline{Data Scientist}}{Sep 2023 -- Dec 2023}
      {\textbf{IBM}}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Fabricated a LLMOps infrastructure using just open-source tools and custom LLM models and deployed the application on Kubernetes using LangServe.}
        \resumeItem{Reduced model hallucination by 30\% and improved faithfulness score by 40\% with advanced prompt engineering and chunking strategies.}
        \resumeItemListEnd

    \resumeSubheading
      {\underline{Data Scientist}}{May 2023 -- July 2023}
      {\textbf{The Globe and Mail}}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Conducted feature engineering on a dataset of over 1 million clickstream data records using PySpark to identify trends used for A/B testing which aided in business analysis.}
        \resumeItem{Undertook News Cycle Analysis on historical data by performing feature extraction using NLP techniques such as Named Entity Recognition (NER) and increased subscription rates by 10\%.}
      \resumeItemListEnd

       \resumeSubheading
      {\underline{Software Engineer}}{May 2022 -- Aug 2022}
      {\textbf{Vivid Seats Inc}}{Toronto, ON}
      \resumeItemListStart
      \resumeItem{Engineered a geolocation microservice in SpringBoot which was integrated by multiple applications.}
        \resumeItem{Developed multiple features for a web application and RESTful APIs for the backend using Next.js and Express to provide seamless communication between 5+ core services.}
      \resumeItemListEnd

      \resumeSubheading
      {\underline{Software Engineer}}{Sep 2021 -- Dec 2021}
      {\textbf{MeazureUp}}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Designed and produced a custom food label printing prototype for BLE devices, resulting in a 60\% increase in restaurant productivity.}
        \resumeItem{Implemented Single Sign-On with OAUTH2 architecture in React Native, improving user efficiency by 20\%.}
      \resumeItemListEnd


  \resumeSubHeadingListEnd


\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://github.com/johndoe/MedChat}{MedChat $|$ Cohere RAG Hackathon 1st place \faPaperclip}}{} 

          \resumeItemListStart
            \resumeItem{Multi-modal chat interface for medical professionals to query medical literature and use AI-powered diagnostic tools.}
            \resumeItem{Leading a team of 5 as a technical product manager to guide for further innovation.}
          \resumeItemListEnd

             \resumeProjectHeading
      {\href{https://github.com/johndoe/Snake-Game-AI}{Snake Game AI $|$ Reinforcement learning \faPaperclip}}{}
          \resumeItemListStart
            \resumeItem{Assembled an agent-based model using Deep Q-Learning with PyTorch and created an environment using PyGame.}
            \resumeItem{Optimized convergence by implementing exploration-exploitation strategies and fine-tuning hyperparameters.}
          \resumeItemListEnd
       
          
    \resumeSubHeadingListEnd


\end{document}
